Gammapy: A Python package for gamma-ray astronomy

### 2023-03-23 src/ms-review.tex
Update src/ms-review.tex

%TODO: better transition into context
% CN: last-minute transition improvement
The Cherenkov Telescope Array Observatory (CTAO) will be the first ground-based
\gammaray instrument to be operated as an open observatory.
Its high-level data\footnote{The lowest reduction level of data published by CTAO will be reconstructed event lists and corresponding instrument response functions.}
will be shared publicly after some proprietary period, along with the software required to analyze them.
The adoption of an open and standardised \gammaray data format, beside being a necesity for future observatories such as \cta,
will be greatly beneficial to the current generation of instruments, eventually allowing to exploit their data legacies even
beyond the end of their scientific operations.

>>>>

%TODO: better transition into context
% CN: last-minute transition improvement
The Cherenkov Telescope Array Observatory (CTAO) will be the first ground-based
\gammaray instrument to be operated as an open observatory.
Its high-level data\footnote{The lowest reduction level of data published by \cta will be reconstructed event lists and corresponding instrument response functions.}
will be shared publicly after some proprietary period, along with the software required to analyze them.
The adoption of an open and standardised \gammaray data format, beside being a necesity for future observatories such as \cta,
will be greatly beneficial to the current generation of instruments, eventually allowing to exploit their data legacies even
beyond the end of their scientific operations.
